|

### 2020-12-03 manuscript/article.Rmd
editing appendix text

---
title:  |
        | The Effect of Legislature Size on Public Spending
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the law of $1/n$ and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find only mixed evidence for the effect of legislature size on government budgets. Yet the aggregate results mask important differences. While earlier, non-causal studies provide moderate support for the law of $1/n$, recent papers using causal inference methods consistently find a negative relation between seats and spending, suggesting that previous results might have been driven by spurious correlations or omitted variable bias. The available evidence also indicates that XXXXXXXXXXXXXXXX"
abstractspacing: onehalf
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
---

@@

\begin{landscape}
\begin{figure}[p]
\begin{center}
\caption{Forest Plots for the Relationship between Legislature Size and Government Spending (Reduced Sample)}
\vspace{.3cm}
\includegraphics[width=25cm,height=17cm]{meta-analysis.pdf}
\label{fig:plots}
\end{center}
\end{figure}
\end{landscape}

@@

@@

In this section, we run a series of meta-regressions with 5 covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries.
Our last covariate is a categorical variable indicating the statistical
procedure used in the original models (panel data, instrumental variables,
OLS, or regression discontinuity design).

Table \ref{tab:regressions} presents the meta-regression results for our
restricted and extended samples. Each column represents one of the three
measures of public spending we discuss in this paper. To reduce the risk of
false positives in our analyses, we use permutation tests to calculate
significance levels for the meta-regressions \citep{higgins2004controlling}.

```latex
\vspace{.5cm}

\begin{table}[htpb]
\caption{Meta Regression Results}
\label{tab:regressions}
\footnotesize
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Independent Variable: $N$ & -2.307 & -5.347 &  -0.280 &  -0.0577 &-0.009 & 0.003\\
                          & (1.490)$\dagger$ & (0.929)*** & (0.162) & (0.073) & (0.005)$\dagger$ & (0.005)\\
%
Independent Variable: log($N$) &  &  &  &  &-0.011& 0.002\\
                               &  &  &  &  & (0.001) & (0.014)\\
%
Year & 0.059 & 0.152 &  0.004 &  0.004 &-0.000& -0.000\\
     & (0.101) & (0.078)* & (0.013) & (0.006) & (0.001) & (0.001)\\
%
Published: No &  &  & 0.200 &  0.103 & 0.0625 & 0.060\\
              &  &  & (0.127) & (0.065) & (0.014)* & (0.016)*\\
%
Non-Majoritarian (PR \& Mixed) & 0.428 & 0.985 & &  & -2.055 & -2.169\\
                               & (0.827) & (0.723)$\dagger$ & &  & (0.283)** & (0.166)***\\
%
Method: Panel & 1.203 & -0.135 & 0.188 & -0.252 & 0.055 & 0.058\\
              & (1.575) & (0.797) & (0.093) & (0.068)*** & (0.013)* & (0.017)*\\
%
Method: IV & 1.317 & 0.186 &  &  &  & \\
           & (1.807) & (0.802) &  &  &  & \\
%
Method: RDD &  &  &  &-0.285&  & \\
            &  &  &  & (0.062)*** &  & \\
% 
Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.001$; ** $p < 0.01$; * $p < 0.05$; $\dagger$ $p < 0.1$.}}
\end{minipage}
\end{table}
```

@@

The meta-regressions indicate that study characteristics have a large influence
on reported results. It is unclear whether factors such as the electoral system
or the level of data aggregation, both believed to moderate the relationship
between legislature size and public expenditure \citep{primo2008distributive,
baqir2002districting, bradbury2003local}, have a substantial impact on the
estimates. We find conflicting evidence for the former and no support for the
latter. Moreover, different statistical techniques produce distinctive results,
which authors should bear in mind.

>>>>

---
title:  |
        | The Effect of Legislature Size on Public Spending
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the law of $1/n$ and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find only mixed evidence for the effect of legislature size on government budgets. Yet the aggregate results mask important differences. While earlier, non-causal studies provide moderate support for the law of $1/n$, recent papers using causal inference methods consistently find a negative relation between seats and spending, suggesting that previous results might have been driven by spurious correlations or omitted variable bias. The available evidence also indicates that XXXXXXXXXXXXXXXX"
abstractspacing: onehalf
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

\begin{landscape}
\begin{figure}[p]
\begin{center}
\caption{Forest Plots for the Relationship between Legislature Size and Government Spending (Reduced Sample)}
\vspace{.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{center}
\end{figure}
\end{landscape}

@@

One reason why we have not detected any effects may be the identification strategy used to estimate the effects. On the one hand, OLS and Panel data models, require too many controls to make units comparable. On the other hand, these techniques are not as credible to estimate the causal effect of legislature size on public expenditures. Estimation methods such as Instrumental Variables, and Regression Discontinuity Design make the units comparable by employing natural and quasi-natural experiments. Figure \ref{fig:plots2} disentangle the estimation techniques for two models that there is broadly variation in the estimation method used: Lower House Size and Expenditure Per Capita (left) and Lower House Size and Log of Expenditure Per Capita (right).[XXXX DANILO CHECAR]

\begin{figure}[htb!]
\begin{center}
\caption{Forest Plots for the Relationship between Legislature Size and Government Spending with Regression Method Heterogeneity (Restricted Sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

Instrumental variables has an interesting variation: from the four coefficients listed, two are positive and two are negative. Two of these four coefficients are significant, again one positive and one negative. The subgroup analysis present a SMD negative but insignificant. When using Regression discontinuity design, the results are uniformily negative. From three papers employing the technique on the natural logarithm of expenditure per capita, all find negative and significant effects. The number of studies, only three, is not enough to predict an overall negative result, but they point in the direction that better identification suggests a zero-to-negative impact of legislature size on expenditure, in support of the reverse "law of $1/n$".[XXXX DANILO CHECAR]

@@

In this section, we run a series of meta-regressions with five covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries.
Our last covariate is a categorical variable indicating the statistical
procedure used in the original models (panel data, instrumental variables,
OLS, or regression discontinuity design).

Table \ref{tabregressions} presents the meta-regression results for our
restricted and extended samples. Each column represents one of the three
measures of public spending we discuss in this paper. To reduce the risk of
false positives in our analyses, we use permutation tests to calculate
significance levels for the meta-regressions \citep{higgins2004controlling}.

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
res <- list()

## Expenditure as percentage GDP -- Restricted
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)

res[[1]] <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Elecsys: Non-Majoritarian",
             "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

## Expenditure as percentage GDP -- Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

res[[2]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Indepvar: logN",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Expenditure per capita - Restricted
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))

res[[3]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Expenditure per capita - Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)

res[[4]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Log of Expenditure per capita - Restricted
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)

res[[5]] <- tibble(
   ` ` = c("Intercept",
           "Indepvar: N",
           "Year",
           "Published: No",
           "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

# Log of Expenditure per capita - Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)

res[[6]] <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "Method: RDD"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
strep <- function (x) {
  ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*','')))
}
```

```{=latex}
\vspace{0.5cm}

\begin{table}[htpb]
\caption{Meta Regression Results\label{tabregressions}}
\footnotesize
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Independent Variable: $N$ & `r round(res[[3]][2,2],3)` & `r round(res[[4]][2,2],3)` & `r round(res[[5]][2,2],3)` & `r round(res[[6]][2,2],3)` & `r round(res[[1]][2,2],3)` & `r round(res[[2]][2,2],3)`\\
                          & (`r round(res[[3]][2,3],3)`)`r strep(res[[3]][2,5])` & (`r round(res[[4]][2,3],3)`)`r strep(res[[4]][2,5])` & (`r round(res[[5]][2,3],3)`)`r strep(res[[5]][2,5])` & (`r round(res[[6]][2,3],3)`)`r strep(res[[6]][2,5])` & (`r round(res[[1]][2,3],3)`)`r strep(res[[1]][2,5])` & (`r round(res[[2]][2,3],3)`)`r strep(res[[2]][2,5])`\\
%
Independent Variable: log($N$) &  &  &  &  & `r round(res[[1]][3,2],3)` & `r round(res[[2]][3,2],3)`\\
                               &  &  &  &  & (`r round(res[[1]][3,3],3)`)`r strep(res[[1]][3,5])` & (`r round(res[[2]][3,3],3)`)`r strep(res[[2]][3,5])`\\
%
Year & `r round(res[[3]][3,2],3)` & `r round(res[[4]][3,2],3)` & `r round(res[[5]][3,2],3)` & `r round(res[[6]][3,2],3)` & `r round(res[[1]][4,2],3)` & `r round(res[[2]][4,2],3)`\\
     & (`r round(res[[3]][3,3],3)`)`r strep(res[[3]][3,5])` & (`r round(res[[4]][3,3],3)`)`r strep(res[[4]][3,5])` & (`r round(res[[5]][3,3],3)`)`r strep(res[[5]][3,5])` & (`r round(res[[6]][3,3],3)`)`r strep(res[[6]][3,5])` & (`r round(res[[1]][4,3],3)`)`r strep(res[[1]][4,5])` & (`r round(res[[2]][4,3],3)`)`r strep(res[[2]][4,5])`\\
%
Published: No & `r round(res[[3]][4,2],3)` & `r round(res[[4]][4,2],3)` & `r round(res[[5]][4,2],3)` &  `r round(res[[6]][4,2],3)` &  & \\
              & (`r round(res[[3]][4,3],3)`)`r strep(res[[3]][4,5])` & (`r round(res[[4]][4,3],3)`)`r strep(res[[4]][4,5])` & (`r round(res[[5]][4,3],3)`)`r strep(res[[5]][4,5])` & (`r round(res[[6]][4,3],3)`)`r strep(res[[6]][4,5])` &  & \\
%
Non-Majoritarian (PR \& Mixed) & `r round(res[[3]][5,2],3)` & `r round(res[[4]][5,2],3)` & &  & `r round(res[[1]][5,2],3)` & `r round(res[[2]][5,2],3)` \\
                               & (`r round(res[[3]][5,3],3)`)`r strep(res[[3]][5,5])` & (`r round(res[[4]][5,3],3)`)`r strep(res[[4]][5,5])` & &  & (`r round(res[[1]][5,3],3)`)`r strep(res[[1]][5,5])` & (`r round(res[[2]][5,3],3)`)`r strep(res[[2]][5,5])`\\
%
Method: Panel & `r round(res[[3]][6,2],3)` & `r round(res[[4]][6,2],3)` & `r round(res[[5]][5,2],3)` & `r round(res[[6]][5,2],3)` & `r round(res[[1]][6,2],3)` & `r round(res[[2]][6,2],3)`\\
              & (`r round(res[[3]][6,3],3)`)`r strep(res[[3]][6,5])` & (`r round(res[[4]][6,3],3)`)`r strep(res[[4]][6,5])` & (`r round(res[[5]][5,3],3)`)`r strep(res[[5]][5,5])` & (`r round(res[[6]][5,3],3)`)`r strep(res[[6]][5,5])` & (`r round(res[[1]][6,3],3)`)`r strep(res[[1]][6,5])` & (`r round(res[[2]][6,3],3)`)`r strep(res[[2]][6,5])`\\
%
Method: IV & `r round(res[[3]][7,2],3)` & `r round(res[[4]][7,2],3)` &  &  &  & \\
           & (`r round(res[[3]][7,3],3)`)`r strep(res[[3]][7,5])` & (`r round(res[[4]][7,3],3)`)`r strep(res[[4]][7,5])` &  &  &  & \\
%
Method: RDD &  &  &  & `r round(res[[6]][6,2],3)` &  & \\
            &  &  &  & (`r round(res[[6]][6,3],3)`)`r strep(res[[6]][6,5])` &  & \\
% 
Intercept & `r round(res[[3]][1,2],3)` & `r round(res[[4]][1,2],3)` & `r round(res[[5]][1,2], 3)` & `r round(res[[6]][1,2], 3)` & `r round(res[[1]][1,2], 3)` & `r round(res[[2]][1,2], 3)`\\
          & (`r round(res[[3]][1,3],3)`)`r strep(res[[3]][1,5])` & (`r res[[4]][1,3]`)`r strep(res[[4]][1,5])` & (`r round(res[[5]][1,3],3)`)`r strep(res[[5]][1,5])` & (`r round(res[[6]][1,3],3)`)`r strep(res[[6]][1,5])` & (`r round(res[[1]][1,3],3)`)`r strep(res[[1]][1,5])` & (`r round(res[[2]][1,3],3)`)`r strep(res[[2]][1,5])`\\
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}
\end{minipage}
\end{table}
```

@@

The meta-regressions indicate that study characteristics have a large influence
on reported results. It is unclear whether factors such as the electoral system
or the level of data aggregation, both believed to moderate the relationship
between legislature size and public expenditure \citep{primo2008distributive,
baqir2002districting, bradbury2003local}, have a substantial impact on the
estimates. We find conflicting evidence for the former and no support for the
latter. Moreover, different statistical techniques produce distinctive results,
with better identified methods (IV and RDD), producing zero and negative effects more frequently.

One may ask why we find no clear-cut evidence in favor or against the theory. The theory renders simple and testable empirical regularities in both of its forms, the "law of $1/n$" and the reverse "law of $1/n$." However, the empirical accessment is far from uniform in its findings. One reason may be the fact that the academic reward in social sciences for accumulating evidence is small, and most papers add features to their theory and further tests while acessing the "law of $1/n$". For instance, in our sample, papers added to the theory supermajority rules [@lee2015supermajority; @lee2016supermajority], redistricting [@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact], coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits], bicameralism [@ricciuti2004legislature], the interplay between upper and lower houses [@chen_malhotra_2007], among others. This has the benefit of enriching the original theory with useful details, but has the disadvantage of providing less clear and decisive tests to the "law of $1/n$" theory. To solve this problem, we need more direct tests of the theory, preferably using well causally identified techniques, such as regression discontinuity design. [XXXX DANILO CHECAR]
